Formalizing Stack Safety as a Security Property

### 2021-09-29 submission4/main.tex
font = 10
Trim space

%% For double-blind review submission, w/o CCS and ACM Reference (max submission space)
\documentclass[12pt,conference]{ieeetran}%\settopmatter{printfolios=true,printccs=false,printacmref=false}

@@

The building blocks of the machine are {\em values} and {\em addresses}.
Both are drawn from some set of {\em words} \(\WORDS\), ranged over by \(\word\) and
\(\addr\), respectively.
%
Our machine states are composed of {\em elements} \(\component\),
which are either addresses or register names (\(\reg\)) drawn from some set
\(\REGS\), which is assumed to include two special-purpose registers: the
program counter {\PCname} and the stack pointer \(\SP\).
A {\em machine state} is a map from elements to values.

\begin{minipage}{.45\columnwidth}
  \[\component \in \COMPONENTS ::= \WORDS + \REGS\]
\vspace{\belowdisplayskip}
\end{minipage}
\begin{minipage}{.45\columnwidth}
  \[\mach \in \MACHS ::= \COMPONENTS \rightarrow \WORDS\]
\vspace{\belowdisplayskip}
\end{minipage}

@@

\section{Case Study: Do Micro-Policies Enforce Stack Safety?}
\label{sec:enforcement}

@@

We validate the micro-policy of the previous section by
systematically testing that it satisfies eager stack integrity and
confidentiality. We use a Coq specification of the RISC-V
architecture\footnote{Available at \url{https://github.com/mit-plv/riscv-coq}.}
%\leo{translated from Haskell via hs-2-coq?\apt{not worth saying since the MIT people did it}}
and extend it with a
runtime monitor implementing the stack-safety
micro-policy. We
  chose the Coq proof assistant as the setting for our implementation
  to ensure that our coinductive trace
  definitions are well-formed, and reason about them, and to leverage the power of the
  QuickChick property-based testing framework~\cite{Pierce:SF4}.

>>>>

%% For double-blind review submission, w/o CCS and ACM Reference (max submission space)
\documentclass[10pt,conference]{ieeetran}%\settopmatter{printfolios=true,printccs=false,printacmref=false}

@@

The building blocks of the machine are {\em values} and {\em addresses}.
Both are drawn from some set of {\em words} \(\WORDS\), ranged over by \(\word\) and
\(\addr\), respectively.
%
Our machine states are composed of {\em elements} \(\component\),
which are either addresses or register names (\(\reg\)) drawn from some set
\(\REGS\), which is assumed to include two special-purpose registers: the
program counter {\PCname} and the stack pointer \(\SP\).
$\component \in \COMPONENTS ::= \WORDS + \REGS$.
A {\em machine state} is a map from elements to values.
$\mach \in \MACHS ::= \COMPONENTS \rightarrow \WORDS$.

@@

\section{Case Study: Micro-Policies}
\label{sec:enforcement}

@@

We validate the micro-policy of the previous section by
systematically testing that it satisfies eager stack integrity and
confidentiality. We use a Coq specification of the RISC-V
architecture\bcp{change from footnote to citation :-)}\footnote{Available at
  \url{https://github.com/mit-plv/riscv-coq}.}
%\leo{translated from Haskell via hs-2-coq?\apt{not worth saying since the MIT people did it}}
and extend it with a
runtime monitor implementing the stack-safety
micro-policy. We
  chose the Coq proof assistant as the setting for our implementation
  to ensure that our coinductive trace
  definitions are well-formed, and reason about them, and to leverage the power of the
  QuickChick property-based testing framework~\cite{Pierce:SF4}.
